Articles Of Association

### 2014-11-17 Articles_of_Association_Melbourne_Bitcoin_Technology_Centre_MBTC_2015.tex
Add additional articles from Swiss Civil Code

@@

      \item The qualifications (if any) for membership of the incorporated association. If there are no specific qualifications for membership, the rules should say so. We recommend that your rules set out how someone applies to become a member; for example by making a request in writing to the secretary of the association.

@@

    \item Membership Fees

@@

@@

@@

      \item The grievance procedures for settling disputes under the rules between the incorporated association and any members or between a member and other member. This procedure must give each party to the dispute an opportunity to be heard on the matter and ensure that an unbiased decision maker decides the outcome of the dispute.

@@

    \item Management Group

@@

      \item The name, membership and powers of the committee or other managing body.

@@

      \item Provision for members to have access to, and to be able to obtain copies of, minutes of general meetings, including financial statements that will be submitted at the association’s annual general meeting.

@@

@@

>>>>

    \item Protection of the objects of the association
      \item No member may be forced against his or her will to accept a change in the objects of the association.

@@

      \item Members may be admitted at any time.
      \item Membership is open to a Natural Persons.
      \item Membership is open to a Legal Entity.
      \item All members have a legal right to resign subject to six months’ notice expiring at the end of the calendar year or, if an administrative period is provided for, at the end of such period.
      \item Membership is neither transferable nor heritable.

@@

    \item Membership Subscription Fees

@@

      \item Members have a duty to pay subscriptions.
      \item D

@@

        \item Any member who has not consented to a resolution which infringes the law or the articles of association is entitled by law to challenge such resolution in court within one month of learning thereof.

@@

      \item If the association lacks one of the prescribed governing bodies, a member or a creditor may apply to the court for an order that the necessary measures be taken.
      \item In particular, the court may set the association a time limit in which to restore the situation required by law and may, if necessary, appoint an administrator.
      \item The association bears the cost of such measures. The court may order the association to make an advance payment to the persons appointed.
      \item For good cause, the association may apply to the court for the removal of the persons it appointed.

@@

    \item Management Comittee

@@

      \item The committee is entitled and obliged as defined under the articles of association to manage and represent the association.
      \item The committee shall maintain the association’s business ledgers.

@@

      \item The committee shall maintain the association’s business ledgers.
      \item Any person may access and produce copies of minutes of meetings.
      \item Any person may access and produce copies of financial statements.

@@

      \item The association is liable for its obligations with its assets. Such liability is limited to the assets.

@@

      \item The association may be dissolved at any time by resolution of the members.
      \item The association is dissolved by operation of law if it is insolvent or if the committee may no longer be appointed in accordance with the articles of association.
      \item By court order where the objects of the association are unlawful or immoral, the competent authority or an interested party may apply for a court order of dissolution.
